Competing Bandits: The Perils of Exploration under Competition

### 2018-09-06 paper/content/barriers.tex
update appendix
Clarified in "barriers".

Our intuition for Finding~\ref{barrier-find}(b) is as follows. Suppose the incumbent switches from \DG to \TS. This switch allows the incumbent to explore actions more efficiently, and therefore should benefit the data advantage. However, the switch increases the reputation cost of exploration in the short run, which could weaken the reputation advantage.

>>>>

Our intuition for Finding~\ref{barrier-find}(b) is as follows. Suppose the incumbent switches from \DG to \TS. This switch allows the incumbent to explore actions more efficiently -- collect better data, not just more data -- and therefore should benefit the data advantage. However, the same switch increases the reputation cost of exploration in the short run, which could weaken the reputation advantage.
